Machine Learning Methods for Site-specific Input Management

### 2022-02-06 Codes/PrepareResults_1.Rmd
Correct the structure of CF_for_VRA folder

```{r, cache = FALSE}
# === packages ===#
library(sf)
library(data.table)
library(RColorBrewer)
library(patchwork)
library(grf)
library(magrittr)
library(ggplot2)
library(ggthemes)
library(viridis)
library(tidyverse)
library(ggpubr)
library(flextable)
library(officer)
library(officedown)
library(modelsummary)
library(here)
library(gridExtra)
library(DiagrammeR)
library(latex2exp)
```

@@

```{r source, results = "hide", fig.show='hide', cache = FALSE }
# setwd(here())
source("./GitControlled/Codes/0_0_functions.R")
# source("./GitControlled/Codes/functions_stepwise_vs_base.R")
```

```{r setup, warning=FALSE, message=FALSE, cache= TRUE}
pCorn <- price_table[2, pCorn]
pN <- price_table[2, pN]

sp_range <- 400

field <- readRDS("./Shared/Data/for_Simulations/field_padding.rds") %>%
    filter(padding==1)%>%
    dplyr::select(unique_cell_id)

####==== (1) cell-level dataset ====####
# coef_data <- readRDS("./Shared/Data/for_Simulations/cnn_coefficients_sprange_400.rds")

# x=1
# coef_data_m <- coef_data[sim == x, ]
# coef_data_t <- coef_data[sim == ifelse(x + 1 >= max(sim), 1, x + 1), ]

# sample_dt <- prepare_raw_data(1, field=field, coef_data_m=coef_data_m, coef_data_t=coef_data_t, app_error="no")

# sample_training_cell <- sample_dt$reg_raw_data

# saveRDS(sample_training_cell, "./Shared/Data/for_writing/sample_reg_raw_data.rds")

field_cell_dt <- readRDS("./Shared/Data/for_writing/sample_reg_raw_data.rds")%>%
    .[,plot_id := ceiling(subplot_id/4)]%>%
    .[padding==1,]

field_cell_sf <- left_join(field, field_cell_dt, by="unique_cell_id")%>%
    na.omit()

# ggplot(field_cell_sf)+
#     geom_sf(aes(fill=factor(padding)), size=0)

##== area of the field ==##
# st_area(st_union(field_cell_sf%>%filter(padding==1)))

# nrow(field_cell_sf)

####==== (2) plot-level dataset without padding area ====####

field_plot_sf <- field_cell_sf%>%
    group_by(plot_id, strip_id, rate)%>%
    summarise()

# nrow(field_plot_sf)
# ggplot(field_plot_sf)+geom_sf()

####==== (3) subplot-level field without padding area ====####

# field_subplot_dt <- field_cell_dt[, .(
#     sim = mean(sim),
#     yield = mean(yield),
#     opt_N = mean(opt_N),
#     rate = mean(rate),
#     aa_n = mean(aa_n), 
#     alpha = mean(alpha),
#     beta = mean(beta),
#     ymax = mean(ymax),
#     alpha1 = mean(alpha1),
#     alpha2 = mean(alpha2),
#     beta1 = mean(beta1),
#     beta2 = mean(beta2),
#     ymax1 = mean(ymax1),
#     ymax2 = mean(ymax2),
#     theta_1 = mean(theta_1),
#     theta_2 = mean(theta_2)
#   ), by = .(subplot_id, strip_id)]%>%
#   .[,unique_subplot_id:=paste0(strip_id,"_",subplot_id)]%>%
#   .[, `:=`(
#     strip_id = NULL,
#     subplot_id = NULL
#   )]

# saveRDS(field_subplot_dt, here("Shared", "Data", "for_writing", "sample_field_subplot_dt.rds"))

field_subplot_dt <- readRDS("Shared/Data/for_writing/sample_field_subplot_dt.rds")

field_subplot_sf <- field_cell_sf%>%
    group_by(subplot_id, strip_id)%>%
    summarise()%>%
    mutate(unique_subplot_id=paste0(strip_id,"_",subplot_id))%>%
    dplyr::select(unique_subplot_id)%>%
    left_join(., field_subplot_dt, by="unique_subplot_id")

# nrow(field_subplot_sf)
# ggplot(field_subplot_sf)+geom_sf()

# Sample CT figure

```{r}

# library(causalTree)
# library(here)
# library(rpart)
# library(rattle)

# ===================================
# Get tree 
# ===================================

# data_sf <- st_read(here("Shared/Data/snider_high_res.gpkg")) %>%
#     na.omit() %>%
#     dplyr::rename(tgtn=NPlan,tgts=SRPlan)

# data_dt <- data.table(data_sf) %>%
#     setnames(names(.),tolower(names(.)))

# tgts_ls <- data_dt[,tgts] %>% unique() %>% sort

# ctree_data <- copy(data_dt) %>%
#   .[tgts %in% tgts_ls[1:2],] %>%
#   .[,treat:=ifelse(tgts==tgts_ls[2],1,0)] %>%
#   #--- Corn Yield: 1 bu/acre ->  62.77 kg/ha---#
#   .[,yield:= yield*62.77]

# tree <- causalTree(
#   yield ~ slope+ecs,
#   data = ctree_data,
#   treatment = ctree_data$treat,
#   split.Rule = "CT",
#   cv.option = "CT",
#   split.Honest = T,
#   cv.Honest = T,
#   split.Bucket = F,
#   xval = 5,
#   cp = 0,
#   minsize = 20,
#   propensity = 0.5
# )

# opcp <- tree$cptable[,1][which.min(tree$cptable[,4])]
# opfit <- prune(tree, opcp)

# pdf(here("GitControlled/Writing/JournalSubmission/ctree_ex.pdf"))
# fancyRpartPlot(opfit,sub='')
# dev.off()

@@

# sample MB curve

```{r, dependson = "setup"}
# gen_yield_MB <- function(ymax, alpha, beta, N) {
#   yield <- ymax * (1 - exp(alpha + beta * N))
#   return(yield)
# }

N_rates <- field_cell_dt[,rate]%>%unique()%>%sort()

N_seq <- 0:300

        # alpha        beta     ymax
# 1: -0.6605052 -0.01572583 10886.94

dt_sample_MB_curve <- field_cell_dt[1,.(alpha,beta,ymax)]%>%
    .[rep(1:nrow(.), each = length(N_seq)), ]%>%
    .[,N:= N_seq]%>%
    .[,Yield := gen_yield_MB(ymax, alpha, beta, N)]

sample_MB_curve <- ggplot()+
    geom_point(data=dt_sample_MB_curve, 
        aes(x=N, y=Yield))+
    theme_few()+
    xlab("N(kg/ha)") + ylab("Yield(kg/ha)")

@@

field_Ndesign <- ggplot() +
    # geom_sf(data=field_plot_sf, color='blue', size=0.8, fill=NA) +
    geom_sf(data=field_plot_sf,
        aes(fill = factor(rate)), size = 0,
        inherit.aes = FALSE,
        # alpha=0.9
        ) +
    scale_fill_viridis_d() +
    labs(fill = "Nitrogen rate\n  (kg/ha)") +
    theme_void()
    # theme(legend.position = "bottom",
    #     legend.title = element_text(size = 0.9))

@@

# yield_dist <- ggplot(field_cell_dt)+
#     geom_density(aes(x=yield))

##== cell level ==##
vis_yield_cell <- ggplot(field_cell_sf) +
    geom_sf(aes(fill = yield), size = 0) +
    scale_fill_viridis_c()+
    labs(fill = "Yield Level\n  (kg/ha)")+
    theme_void()

##== subplot yield level ==##
vis_yield_subplot <- ggplot(field_subplot_sf) +
    geom_sf(aes(fill = yield), size = 0) +
    scale_fill_viridis_c()+
    labs(fill = "Yield Level\n  (kg/ha)")+
    theme_void()

@@

```{r, dependson = "setup"}
opt_N_dist <- ggplot(field_cell_dt)+
    geom_density(aes(x=opt_N))

##== cell level ==##
vis_optN_cell <- ggplot(field_cell_sf) +
    geom_sf(aes(fill = opt_N), size = 0) +
    scale_fill_viridis_c()+
    labs(fill = "EONR (kg/ha)")+
    theme_void()

##== subplot yield level ==##
vis_optN_subplot <- ggplot(field_subplot_sf) +
    geom_sf(aes(fill = opt_N), size = 0) +
    scale_fill_viridis_c()+
    labs(fill = "Yield Level\n  (kg/ha)")+
    theme_void()
```

@@

```{r, dependson = "setup"}
####==== ymax map ====####
ymax_dist <- ggplot(field_cell_dt)+
    geom_density(aes(x=ymax))

field_ymax <- ggplot(field_cell_sf) +
    geom_sf(aes(fill = ymax), size = 0) +
    scale_fill_viridis_c()+
    ggtitle('(1) ymax')+
    labs(fill = "kg/ha")+
    theme_void()
    # theme(legend.title = element_blank())

####==== alpha map ====####
alpha_dist <- ggplot(field_cell_dt)+
    geom_density(aes(x=alpha))

field_alpha <- ggplot(field_cell_sf) +
    geom_sf(aes(fill = alpha), size = 0) +
    scale_fill_viridis_c() +
    ggtitle(expression("(2) " ~alpha)) +
    theme_void() +
    theme(legend.title = element_blank())

####==== beta map ====####
beta_dist <- ggplot(field_cell_dt)+
    geom_density(aes(x=beta))

field_beta <- ggplot(field_cell_sf) +
    geom_sf(aes(fill = beta), size = 0) +
    scale_fill_viridis_c()+
    ggtitle(expression("(3) " ~beta)) +
    # labs(fill = expression(~beta))+
    theme_void() +
    theme(legend.title = element_blank())

@@

field_m_error <- ggplot(field_cell_sf) +
    geom_sf(aes(fill = yield_error), size = 0) +
    scale_fill_viridis_c()+
    ggtitle(expression("(d) " ~epsilon)) +
    labs(fill = "kg/ha")+
    theme_void()
    # theme(legend.title = element_blank())

@@

```{r source-results, message=FALSE, warning=FALSE, cache= TRUE}

@@

## Report R^2 of of Predicted Yield (RF, BRF, CNN)

@@

```{r}
# rmse_y_all_v2 <- rmse_y_all %>%
#     .[,`:=`(
#         rmse_y_scale = scales::rescale(rmse_y),
#         rmse_optN_scale = scales::rescale(rmse_optN)
#         ), by= .(Model, Method)]

fig_y_optN <- rmse_y_all[Method %in% c("RF", "BRF", "CNN")] %>%
    ggplot(aes(x=rmse_y, y=rmse_optN))+
    geom_point(size=0.5)+
    facet_grid(Model ~ Method) +
    # geom_smooth(method='lm', se=FALSE,  aes(colour="Regression line"), size=1) +
    # scale_colour_manual(values= "red") +
    geom_smooth(method='lm', se=FALSE,  color = "red", size=1) +
    stat_regline_equation(
        # label.x.npc = "right",
        # label.y.npc = "top", 
        label.x = 2150, label.y = 85,
        aes(label = ..rr.label..)) +
    # geom_abline(slope=1, intercept=0, color="red")+
    guides(
        fill = guide_legend(keywidth = 1, keyheight = 1),
        linetype = guide_legend(keywidth = 3, keyheight = 1),
        colour= guide_legend(keywidth = 3, keyheight = 1))+
    labs(y = " RMSE of EONR Estimation (kg/ha)")+
    labs(x = " RMSE of Yield Prediction (kg/ha)")+
    theme_few() +
    theme(
        strip.text.x = element_text(size=12,face="bold"),
        strip.text.y = element_text(size=12,face="bold"),
        legend.title = element_blank(),
        legend.text = element_text(size=12, face="bold"),
        legend.position = "bottom")

# print(fig_y_optN, preview = "docx")
# dfabline <- data.frame(
#     x = 0:3500, y=0:3500)

# figure_te <- readRDS(here("Shared/Data/for_writing/dt_TEcomparison.rds"))%>%
#     .[, Method:= case_when(
#         Method=="RF" ~ "RF",
#         Method=="BRF" ~ "BRF",
#         Method=="CF_base" ~ "CF-base")] %>%
#     .[, Method:= factor(Method, levels = c("RF", "BRF", "CF-base"))]%>%
#     ggplot() +
#     geom_point(aes(x=true_tau_base, y=tau_base), size=0.5)+
#     # geom_abline(aes(intercept = 0, slope = 1, color = "1-to-1 line"), show.legend=TRUE) +
#     geom_line(data=dfabline, aes(x=x, y=y, color="1-to-1 line")) +
#     scale_colour_manual(labels = "1-to-1 line", values="red") +
#     facet_grid(Treatment ~ Method) +
#     guides(
#         fill = guide_legend(keywidth = 1, keyheight = 1),
#         linetype = guide_legend(keywidth = 3, keyheight = 1),
#         colour= guide_legend(keywidth = 3, keyheight = 1),
#         direction = "horizontal")+
#     labs(y = "Estimated Treatment Effect")+
#     labs(x = "True Treatment Effect")+
#     theme_few() +
#     theme(
#         strip.text.x = element_text(size=12,face="bold"),
#         strip.text.y = element_text(size=12,face="bold"),
#         legend.title = element_blank(),
#         legend.text = element_text(size=12, face="bold"),
#         legend.position = "bottom")

@@

    # # RF vs BRF
    # .[,rmse_y_ratio_RF_BRF := rmse_y_RF/rmse_y_BRF]%>%
    # .[,rmse_optN_ratio_RF_BRF := rmse_optN_RF/rmse_optN_BRF]%>%
    # # CNN vs RF
    # .[,rmse_y_ratio_CNN_RF := rmse_y_CNN/rmse_y_RF]%>%
    # .[,rmse_optN_ratio_CNN_RF := rmse_optN_CNN/rmse_optN_RF]%>%
    # # CNN vs BRF 
    # .[,rmse_y_ratio_CNN_BRF := rmse_y_CNN/rmse_y_BRF]%>%
    # .[,rmse_optN_ratio_CNN_BRF := rmse_optN_CNN/rmse_optN_BRF]

# nrow(.SD[ML_cnst_y_piLoss=="BRF"])
# prepare_count_tab[ML_cnst_y_piLoss=="RF",] %>% nrow()
# prepare_count_tab[ML_cnst_y_piLoss=="BRF",] %>% nrow()
# prepare_count_tab[ML_cnst_y_piLoss=="CNN",] %>% nrow()

# Summary Table 
summary_res_CNN_RF_BRF <- prepare_count_tab%>%
    .[,.(
        count_BRF = nrow(.SD[ML_cnst_y_piLoss=="BRF",]),
        count_RF = nrow(.SD[ML_cnst_y_piLoss=="RF",]),
        count_CNN = nrow(.SD[ML_cnst_y_piLoss=="CNN",]),
        count_y_BRF = nrow(.SD[which_ML_y=="BRF",]),
        count_y_RF = nrow(.SD[which_ML_y=="RF",]),
        count_y_CNN = nrow(.SD[which_ML_y=="CNN",]),
        Total= sum(index_cnst_y_piLoss)
        ), by=Model] %>%
    .[,`:=`(
         blank1 = NA, blank2 = NA, blank3 = NA, blank4 = NA
        )] %>%
    .[,.(Model, blank1, count_y_RF, count_RF,  blank2, count_y_BRF, count_BRF, blank3, count_y_CNN, count_CNN ,blank4, Total)]

# summary_res_CNN_RF_BRF[Model=="aby", count_y_RF]

#- table creation -#
report_summary_res_CNN_RF_BRF <- copy(summary_res_CNN_RF_BRF)%>%
    flextable(.) %>%
    border_remove() %>%
    delete_part(part = "header") %>%
    add_header(
        Model="Model", 
        blank1 = "", count_y_RF = "RF", count_RF = "RF",
        blank2 = "", count_y_BRF = "BRF", count_BRF = "BRF",
        blank3 = "", count_y_CNN = "CNN", count_CNN = "CNN",
        blank4 = "", Total = "Total",
        top = TRUE) %>%
    merge_h(part = "header") %>%
    hline_bottom(j=c(3:4, 6:7, 9:10), part = "header") %>%
    add_header(
        Model="", 
        blank1 = "", count_y_RF = "#Y", count_RF = "#YP",
        blank2 = "", count_y_BRF = "#Y", count_BRF = "#YP",
        blank3 = "", count_y_CNN = "#Y", count_CNN = "#YP",
        blank4 = "", Total = "",
        top = FALSE) %>%
    hline_bottom(part="all") %>%
    hline_top(part="header") %>%
    align(align = "center", part = "all")%>%
    align(j=1,  align = "left", part = "all")%>%
    footnote(
    value = as_paragraph("NOTE: #Y indicates the number of simulation rounds in which the model provided the lowest RMSE for yield prediction. #YP indicates the number of simulation rounds in which the model provided the lower RMSE of yield prediction and the highest profit at the same time."),
     ref_symbols = NA
    ) %>%
    # set_table_properties(width = .7, layout = "autofit") %>%
    fontsize(i = NULL, j = NULL, size = 9, part = "footer") %>%
    autofit() %>%
    width(j = c(3,4,6,7,9,10,12), width=0.6)%>%
    width(j = c(2,5,8,11), width=0.1)

    # set_table_properties(width = .6, layout = "autofit")

# print(report_summary_res_CNN_RF_BRF, preview = "docx")
# in terms of RMSE of yield prediction and ", "\U1D70B\U0302", as_sub("loss"), ", respectively.

@@

##== Distribution ==##
plot_dis_optN <- copy(report_res_subsetML)%>%
    .[Method %in% c("RF", "BRF", "CF_base"), ]%>%
    .[, Method := case_when(
    # Method == "CF_stepwise" ~ "CF-stepwise",
    Method == "CF_base" ~ "CF-base",
    Method == "RF" ~ "RF",
    Method == "BRF" ~ "BRF"
    )]%>%
    .[, Model := case_when(
    Model == "aby" ~ "Scenario: aby",
    Model == "abytt" ~ "Scenario: abytt",
    Model == "aabbyy" ~ "Scenario: aabbyy",
    Model == "aabbyytt" ~ "Scenario: aabbyytt"
    )]%>%
    # .[, Method:=factor(Method, levels = c("RF", "BRF", "CF-stepwise", "CF-base"))]%>%
    .[, Method:=factor(Method, levels = c("RF", "BRF", "CF-base"))]%>%
    .[, Model:=factor(Model, 
        levels = c("Scenario: aby", "Scenario: abytt", "Scenario: aabbyy", "Scenario: aabbyytt"))] %>%
    ggplot()+
    geom_density(aes(x=rmse_optN, fill=Method), alpha=0.7)+
    # scale_fill_viridis_d()+
    facet_wrap(~Model, ncol = 1)+
    # labs(x = expression(R^2))+
    labs(x = "RMSE (kg/ha)")+
    theme_few()+
    theme(
        strip.text.x = element_text(size=12,face="bold"),
        legend.title = element_text(size=12,face="bold"),
        legend.text = element_text(size=12, face="bold"),
        legend.position = "bottom")

##== Summary Table  ==##

#- preparation -#
table_optN_prep <- copy(report_res_subsetML)%>%
    .[, .(
        rmse_optN = mean(rmse_optN),
        pi_loss = mean(Mean)
        ), by=.(Method, Model)]%>%
    .[,`:=`(
        rmse_optN = format(round(rmse_optN,1), nsmall=1),
        pi_loss = format(round(pi_loss,2), nsmall=2)
        )] %>%
    dcast(Model~Method, value.var = c("rmse_optN", "pi_loss")) %>%
    .[,`:=`(
         blank1 = NA, blank2 = NA, blank3 = NA, blank4 = NA, blank5 = NA
        )] %>%
    .[,.(Model, blank1, rmse_optN_RF, pi_loss_RF,  blank2, rmse_optN_BRF, pi_loss_BRF, blank3, rmse_optN_CNN, pi_loss_CNN ,blank4, rmse_optN_CF_base, pi_loss_CF_base)]

# table_optN_prep[Model=="aby", rmse_optN_RF]

# avg_optN <- copy(report_res_subsetML)%>%
#     .[, .(
#         Avg_rmse_optN = mean(rmse_optN),
#         Avg_pi_loss = mean(Mean)
#         ), by=Method] %>%
#     .[, `:=`(
#         Avg_rmse_optN = format(round(Avg_rmse_optN, digits=1), nsmall = 1),
#         Avg_pi_loss = format(round(Avg_pi_loss, digits=2), nsmall=2)
#         )]

#- table creation -#
report_table_optN <- copy(table_optN_prep)%>%
    mutate(
    across(
      everything(),
      as.character
        )
    )%>%
    # add_row(.after = 4) %>%
    flextable(.) %>%
    border_remove() %>%
    delete_part(part = "header") %>%
    add_header(
       Model="Model", 
        blank1 = "", rmse_optN_RF = "RF", pi_loss_RF = "RF",
        blank2 = "", rmse_optN_BRF = "BRF", pi_loss_BRF = "BRF",
        blank3 = "", rmse_optN_CNN = "CNN", pi_loss_CNN = "CNN",
        blank4 = "", rmse_optN_CF_base = "CF-base", pi_loss_CF_base = "CF-base",
        top = TRUE) %>%
    merge_h(part = "header") %>%
    hline_bottom(j=c(3:4, 6:7, 9:10, 12:13), part = "header") %>%
    add_header(
       Model="", 
        blank1 = "", rmse_optN_RF = "RMSE", pi_loss_RF = "pi_loss",
        blank2 = "", rmse_optN_BRF = "RMSE", pi_loss_BRF = "pi_loss",
        blank3 = "", rmse_optN_CNN = "RMSE", pi_loss_CNN = "pi_loss",
        blank4 = "", rmse_optN_CF_base = "RMSE", pi_loss_CF_base = "pi_loss",
        top = FALSE) %>%
    compose(i = 2, j = c(4, 7, 10, 13), part = "header", value = as_paragraph("\U1D70B\U0302", as_sub(as_i("def")))) %>%
    hline_bottom(part="all") %>%
    hline_top(part="header") %>%
    align(align = "center", part = "all")%>%
    align(j=1,  align = "left", part = "all")%>%
    # autofit() %>%
    # width(j = c(2,5,8,11), width=0.3) %>%
    # fix_border_issues() 
    footnote(
        # i = 1, j = c(4, 7, 10, 13), part = "header",
    value = as_paragraph("NOTE: \U1D70B\U0302", as_sub(as_i("def")), " indicates profit-deficit ($/ha) relative to the true maximum profit at the subplot level. The maximized profit is the profit under the true yield response functions evaluated at ", as_i("\U004E\U2071"), as_sub(as_i("opt")),"."),
     ref_symbols = NA
    ) %>%
    fontsize(i = NULL, j = NULL, size = 9, part = "footer") %>%
    autofit() %>%
    width(j = c(3,4,6,7,9,10,12,13), width=0.6)%>%
    width(j = c(2,5,8,11), width=0.1)

    # print(report_table_optN, preview = "docx")
    # autofit() 
    # width(j = c(2,5,8,11), width=0.5)
    # width(j = c(2,5,8,11), width=0.5)

# print(report_table_optN, preview = "docx")

# typology <- data.frame(
#   col_keys = names(table_optN_prep),
#   what = c(" ", " ", "RF", "RF", " ", "BRF", "BRF", " ", "CNN", "CNN", " ", "CF-base", "CF-base"),
#   measure = c(" ", " ", "RMSE", "pi_loss", " ", "RMSE", "pi_loss", " ", "RMSE", "pi_loss", " ", "RMSE", "pi_loss"),
#   stringsAsFactors = FALSE )

>>>>

```{r, cache = FALSE}
# === packages ===#
# --- data wrangling--- #
library(sf)
library(data.table)
library(tidyverse)

# --- figure making --- #
library(RColorBrewer)
library(patchwork)
library(ggplot2)
library(ggthemes)
library(viridis)
library(ggpubr)
library(gridExtra)
library(DiagrammeR)

# --- table making --- #
library(flextable)
library(officer)
library(officedown)
library(modelsummary)
library(latex2exp)
```

@@

<!-- ```{r source, results = "hide", fig.show='hide', cache = FALSE }
# setwd(here())
# source("./GitControlled/Codes/0_0_functions.R")
``` -->

```{r setup, warning=FALSE, message=FALSE, cache= FALSE}
# field <- readRDS("./Shared/Data/for_Simulations/field_padding.rds") %>%
#     filter(padding==1)%>%
#     dplyr::select(unique_cell_id)

# === plot-level field data set  === #
field_plot_sf <- readRDS("./Shared/Results/for_writing/sample_field_plot_sf.rds")
# === subplot-level field data set  === #
field_subplot_sf <- readRDS("./Shared/Results/for_writing/sample_field_subplot_sf.rds")
# === cell-level field data set  === #
field_cell_sf <- readRDS("./Shared/Results/for_writing/sample_field_cell_sf.rds")
```

# Variogram Prameter Table

@@

@@

```{r, dependson = "setup"}
field_Ndesign <- ggplot() +
    geom_sf(data=field_plot_sf,
        aes(fill = factor(rate)), size = 0,
        inherit.aes = FALSE,
        ) +
    scale_fill_viridis_d() +
    labs(fill = "Nitrogen rate\n  (kg/ha)") +
    theme_void()
```

@@

# === cell-level === #
vis_yield_cell <- ggplot(field_cell_sf) +
    geom_sf(aes(fill = yield), size = 0) +
    scale_fill_viridis_c()+
    labs(fill = "Yield Level\n  (kg/ha)")+
    theme_void()

# === subplot-level === #
vis_yield_subplot <- ggplot(field_subplot_sf) +
    geom_sf(aes(fill = yield), size = 0) +
    scale_fill_viridis_c()+
    labs(fill = "Yield Level\n  (kg/ha)")+
    theme_void()
```

@@

# === cell-level === #
vis_optN_cell <- ggplot(field_cell_sf) +
    geom_sf(aes(fill = opt_N), size = 0) +
    scale_fill_viridis_c()+
    labs(fill = "EONR (kg/ha)")+
    theme_void()
```

@@

```{r, dependson = "setup"}
####==== ymax map ====####
field_ymax <- ggplot(field_cell_sf) +
    geom_sf(aes(fill = ymax), size = 0) +
    scale_fill_viridis_c()+
    ggtitle('(1) ymax')+
    labs(fill = "kg/ha")+
    theme_void()

####==== alpha map ====####
field_alpha <- ggplot(field_cell_sf) +
    geom_sf(aes(fill = alpha), size = 0) +
    scale_fill_viridis_c() +
    ggtitle(TeX("(2)  $\\alpha$")) +
    # ggtitle(expression("(2) " ~alpha)) +
    theme_void() +
    theme(legend.title = element_blank())

####==== beta map ====####
field_beta <- ggplot(field_cell_sf) +
    geom_sf(aes(fill = beta), size = 0) +
    scale_fill_viridis_c()+
    ggtitle(TeX("(3)  $\\beta$")) +
    theme_void() +
    theme(legend.title = element_blank())

@@

field_m_error <- ggplot(field_cell_sf) +
    geom_sf(aes(fill = yield_error), size = 0) +
    scale_fill_viridis_c()+
    ggtitle(TeX("(4)  $\\epsilon$")) +
    labs(fill = "kg/ha")+
    theme_void()

@@

```{r source-results, message=FALSE, warning=FALSE, cache= FALSE}

@@

## Report RMSE of of Yield Prediction (RF, BRF, CNN)

@@

```{r}
fig_y_optN <- rmse_y_all[Method %in% c("RF", "BRF", "CNN")] %>%
    ggplot(aes(x=rmse_y, y=rmse_optN))+
    geom_point(size=0.5)+
    facet_grid(Model ~ Method) +
    # geom_smooth(method='lm', se=FALSE,  aes(colour="Regression line"), size=1) +
    # scale_colour_manual(values= "red") +
    geom_smooth(method='lm', se=FALSE,  color = "red", size=1) +
    stat_regline_equation(
        # label.x.npc = "right",
        # label.y.npc = "top", 
        label.x = 2150, label.y = 85,
        aes(label = ..rr.label..)) +
    # geom_abline(slope=1, intercept=0, color="red")+
    guides(
        fill = guide_legend(keywidth = 1, keyheight = 1),
        linetype = guide_legend(keywidth = 3, keyheight = 1),
        colour= guide_legend(keywidth = 3, keyheight = 1))+
    labs(y = " RMSE of EONR Estimation (kg/ha)")+
    labs(x = " RMSE of Yield Prediction (kg/ha)")+
    theme_few() +
    theme(
        strip.text.x = element_text(size=12,face="bold"),
        strip.text.y = element_text(size=12,face="bold"),
        legend.title = element_blank(),
        legend.text = element_text(size=12, face="bold"),
        legend.position = "bottom")

# print(fig_y_optN, preview = "docx")
# dfabline <- data.frame(x = 0:3500, y=0:3500)

@@

# === Summary Table === #
summary_res_CNN_RF_BRF <- prepare_count_tab%>%
    .[,.(
        count_BRF = nrow(.SD[ML_cnst_y_piLoss=="BRF",]),
        count_RF = nrow(.SD[ML_cnst_y_piLoss=="RF",]),
        count_CNN = nrow(.SD[ML_cnst_y_piLoss=="CNN",]),
        count_y_BRF = nrow(.SD[which_ML_y=="BRF",]),
        count_y_RF = nrow(.SD[which_ML_y=="RF",]),
        count_y_CNN = nrow(.SD[which_ML_y=="CNN",]),
        Total= sum(index_cnst_y_piLoss)
        ), by=Model] %>%
    .[,`:=`(
         blank1 = NA, blank2 = NA, blank3 = NA, blank4 = NA
        )] %>%
    .[,.(Model, blank1, count_y_RF, count_RF,  blank2, count_y_BRF, count_BRF, blank3, count_y_CNN, count_CNN ,blank4, Total)]

# === Table creation === #
report_summary_res_CNN_RF_BRF <- copy(summary_res_CNN_RF_BRF)%>%
    flextable(.) %>%
    border_remove() %>%
    delete_part(part = "header") %>%
    add_header(
        Model="Model", 
        blank1 = "", count_y_RF = "RF", count_RF = "RF",
        blank2 = "", count_y_BRF = "BRF", count_BRF = "BRF",
        blank3 = "", count_y_CNN = "CNN", count_CNN = "CNN",
        blank4 = "", Total = "Total",
        top = TRUE) %>%
    merge_h(part = "header") %>%
    hline_bottom(j=c(3:4, 6:7, 9:10), part = "header") %>%
    add_header(
        Model="", 
        blank1 = "", count_y_RF = "#Y", count_RF = "#YP",
        blank2 = "", count_y_BRF = "#Y", count_BRF = "#YP",
        blank3 = "", count_y_CNN = "#Y", count_CNN = "#YP",
        blank4 = "", Total = "",
        top = FALSE) %>%
    hline_bottom(part="all") %>%
    hline_top(part="header") %>%
    align(align = "center", part = "all")%>%
    align(j=1,  align = "left", part = "all")%>%
    footnote(
    value = as_paragraph("NOTE: #Y indicates the number of simulation rounds in which the model provided the lowest RMSE for yield prediction. #YP indicates the number of simulation rounds in which the model provided the lower RMSE of yield prediction and the highest profit at the same time."),
     ref_symbols = NA
    ) %>%
    # set_table_properties(width = .7, layout = "autofit") %>%
    fontsize(i = NULL, j = NULL, size = 9, part = "footer") %>%
    autofit() %>%
    width(j = c(3,4,6,7,9,10,12), width=0.6)%>%
    width(j = c(2,5,8,11), width=0.1)
```

@@

# === Distribution of RMSE of EONR estimates === #

plot_dis_optN <- copy(report_res_subsetML)%>%
    .[Method %in% c("RF", "BRF", "CF_base"), ]%>%
    .[, Method := case_when(
    # Method == "CF_stepwise" ~ "CF-stepwise",
    Method == "CF_base" ~ "CF-base",
    Method == "RF" ~ "RF",
    Method == "BRF" ~ "BRF"
    )]%>%
    .[, Model := case_when(
    Model == "aby" ~ "Scenario: aby",
    Model == "abytt" ~ "Scenario: abytt",
    Model == "aabbyy" ~ "Scenario: aabbyy",
    Model == "aabbyytt" ~ "Scenario: aabbyytt"
    )]%>%
    # .[, Method:=factor(Method, levels = c("RF", "BRF", "CF-stepwise", "CF-base"))]%>%
    .[, Method:=factor(Method, levels = c("RF", "BRF", "CF-base"))]%>%
    .[, Model:=factor(Model, 
        levels = c("Scenario: aby", "Scenario: abytt", "Scenario: aabbyy", "Scenario: aabbyytt"))] %>%
    ggplot()+
    geom_density(aes(x=rmse_optN, fill=Method), alpha=0.7)+
    # scale_fill_viridis_d()+
    facet_wrap(~Model, ncol = 1)+
    # labs(x = expression(R^2))+
    labs(x = "RMSE (kg/ha)")+
    theme_few()+
    theme(
        strip.text.x = element_text(size=12,face="bold"),
        legend.title = element_text(size=12,face="bold"),
        legend.text = element_text(size=12, face="bold"),
        legend.position = "bottom")

# === Summary Table === #

# --- prepation --- #
table_optN_prep <- copy(report_res_subsetML)%>%
    .[, .(
        rmse_optN = mean(rmse_optN),
        pi_loss = mean(Mean)
        ), by=.(Method, Model)]%>%
    .[,`:=`(
        rmse_optN = format(round(rmse_optN,1), nsmall=1),
        pi_loss = format(round(pi_loss,2), nsmall=2)
        )] %>%
    dcast(Model~Method, value.var = c("rmse_optN", "pi_loss")) %>%
    .[,`:=`(
         blank1 = NA, blank2 = NA, blank3 = NA, blank4 = NA, blank5 = NA
        )] %>%
    .[,.(Model, blank1, rmse_optN_RF, pi_loss_RF,  blank2, rmse_optN_BRF, pi_loss_BRF, blank3, rmse_optN_CNN, pi_loss_CNN ,blank4, rmse_optN_CF_base, pi_loss_CF_base)]

#- table creation -#
report_table_optN <- copy(table_optN_prep)%>%
    mutate(
    across(
      everything(),
      as.character
        )
    )%>%
    # add_row(.after = 4) %>%
    flextable(.) %>%
    border_remove() %>%
    delete_part(part = "header") %>%
    add_header(
       Model="Model", 
        blank1 = "", rmse_optN_RF = "RF", pi_loss_RF = "RF",
        blank2 = "", rmse_optN_BRF = "BRF", pi_loss_BRF = "BRF",
        blank3 = "", rmse_optN_CNN = "CNN", pi_loss_CNN = "CNN",
        blank4 = "", rmse_optN_CF_base = "CF-base", pi_loss_CF_base = "CF-base",
        top = TRUE) %>%
    merge_h(part = "header") %>%
    hline_bottom(j=c(3:4, 6:7, 9:10, 12:13), part = "header") %>%
    add_header(
       Model="", 
        blank1 = "", rmse_optN_RF = "RMSE", pi_loss_RF = "pi_loss",
        blank2 = "", rmse_optN_BRF = "RMSE", pi_loss_BRF = "pi_loss",
        blank3 = "", rmse_optN_CNN = "RMSE", pi_loss_CNN = "pi_loss",
        blank4 = "", rmse_optN_CF_base = "RMSE", pi_loss_CF_base = "pi_loss",
        top = FALSE) %>%
    compose(i = 2, j = c(4, 7, 10, 13), part = "header", value = as_paragraph("\U1D70B\U0302", as_sub(as_i("def")))) %>%
    hline_bottom(part="all") %>%
    hline_top(part="header") %>%
    align(align = "center", part = "all")%>%
    align(j=1,  align = "left", part = "all")%>%
    # autofit() %>%
    # width(j = c(2,5,8,11), width=0.3) %>%
    # fix_border_issues() 
    footnote(
        # i = 1, j = c(4, 7, 10, 13), part = "header",
    value = as_paragraph("NOTE: \U1D70B\U0302", as_sub(as_i("def")), " indicates profit-deficit ($/ha) relative to the true maximum profit at the subplot level. The maximized profit is the profit under the true yield response functions evaluated at ", as_i("\U004E\U2071"), as_sub(as_i("opt")),"."),
     ref_symbols = NA
    ) %>%
    fontsize(i = NULL, j = NULL, size = 9, part = "footer") %>%
    autofit() %>%
    width(j = c(3,4,6,7,9,10,12,13), width=0.6)%>%
    width(j = c(2,5,8,11), width=0.1) 
```
